Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
Title and abstract.

% Document starts
\begin{document}
% Title portion. Note the short title for running heads
\title{Improving credibility and efficiency of decision-making within democratic communities via a statistical quorum}

@@

\begin{abstract}
The Achilles heel of many major democracies is the perpetual need for sufficient engagement and attention from the community. While there have been major efforts towards increasing these attributes within the community, we explore a fundamentally different approach: For a fixed level of community attention, how can we optimize the allocation of this attention to maximize productivity? We propose a novel \textit{statistical quorum}, derived using first principles, as one metric the community can use to focus attention, in turn making the entire decision-making process dynamic. We developed a web application centered around this metric and tested it in a 140-person community that holds weekly councils over the course of 16 weeks. We found that the community was able to use the web application to simultaneously improve the credibility and efficiency of their decision-making process.
\end{abstract}

>>>>

% Document starts
\begin{document}
% Title portion. Note the short title for running heads
\title[Improving credibility and efficiency of decision-making]{Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum}

@@

\begin{abstract}
The Achilles heel of many major democracies is the eternal need for sufficient engagement and attention from the community.
While there have been major efforts towards increasing these attributes within the community, we explore a fundamentally
different approach: For a fixed level of community attention, how can we optimize the allocation of this attention to
maximize productivity?
We propose a novel \textit{statistical quorum}, derived using first principles, as one metric the community can use to
focus attention, in turn making the entire decision-making process dynamic.
We developed a web application centered around this metric and tested it in a 140-person community that holds weekly
councils over the course of 16 weeks.
We found that the community was able to use the web application to simultaneously improve the credibility and efficiency
of their decision-making process.
\end{abstract}
